Figures

### 2016-09-09 ms_1_intro.Rmd
asdf

The fundamental differences between the datasets (EOO versus AOO, measure of range size versus distribution) suggest that the choice of one over the other should be carefully matched to the purpose for which it is to be used [@GastonXXX 2008, XXX Other refs], and yet these datasets have been used in hundreds of studies and applications for a wide range of purposes, including assessing marine species status [@halpern_index_2012; @halpern_patterns_2015; @selig_assessing_2013-1], evaluating global biodiversity patterns [@coll_biodiversity_2010; @martin_manual_2014; @pimm_biodiversity_2014; @kaschner_current_2011], predicting species range shifts [@garciamolinos_climate_2015], and setting conservation priorities [@klein_shortfalls_2015].  In most of these cases, the implications of choosing one versus the other of these datasets is not evaluated or discussed, yet strong conservation and management conclusions are drawn from the results of the studies.

@@

Here we focus not on how the two datasets should ideally be used; instead, in recognizing that each provides value for many aspects of conservation research, we highlight hidden assumptions and sources of error within each dataset, and explore the implications of choosing one over the other.

@@

@@

As a case study, we then reexamine a global analysis of gaps in protection afforded by marine protected areas (MPAs) [@klein_shortfalls_2015] as a case study to explore the implications of selecting one data set over the other.  Repeating the study using IUCN range data rather than AquaMaps data increases the apparent proportion of gap species from 1.4% to 6.4%, while also increasing the proportion of well-protected species from 1.5% to 2.9%.  This shift highlights the implications of different data use decisions on our understanding of marine biodiversity status and protection.

>>>>

_paragraph describing IUCN and AM as EOO and AOO respectively, with basic defs and implication that AM will generally be smaller than IUCN; possibly refer to Table S1 for defs and details?_ _one reference: http://www.biodiversitya-z.org/content/species-extent-of-occurrence-eoo "The intent behind this parameter is to measure the degree to which risks from threatening factors are spread spatially across the taxon’s geographical distribution. It is not intended to be an estimate of the amount of occupied or potential habitat, or a general measure of the taxon’s range" and http://www.biodiversitya-z.org/content/species-area-of-occupancy-aoo "The measure reflects the fact that a taxon will not usually occur throughout the area of its extent of occurrence, which may, for example, contain unsuitable habitats"_

The fundamental differences between the datasets suggest that the choice of one over the other should be carefully matched to the purpose for which it is to be used [@GastonXXX 2008, XXX Other refs], and yet these datasets have been used in hundreds of studies and applications for a wide range of purposes, including assessing marine species status [@halpern_index_2012; @halpern_patterns_2015; @selig_assessing_2013-1], evaluating global biodiversity patterns [@coll_biodiversity_2010; @martin_manual_2014; @pimm_biodiversity_2014; @kaschner_current_2011], predicting species range shifts [@garciamolinos_climate_2015], and setting conservation priorities [@klein_shortfalls_2015].  In most of these cases, the implications of choosing one versus the other of these datasets is not evaluated or discussed, yet strong conservation and management conclusions are drawn from the results of the studies.

@@

Here we focus not on how the two datasets should ideally be used; instead, in recognizing that each provides value for many aspects of conservation research, we highlight hidden assumptions and sources of error within each dataset, and explore the implications of choosing one over the other.  _You science with the data you have, not with the data you wish you had.  Often, the ideal type of spatial data is not always available, and non-ideal data is better than no data at all.  In such a case, it is crucial to acknowledge, and where possible address, the resulting tradeoffs._

@@

___maybe here, based on EOO/AOO defs, we expect AM to generally fall within, and describe a smaller range than, IUCN; where the two disagree, that's where it gets interesting___

@@

As a case study, we then reexamine a global analysis of gaps in protection afforded by marine protected areas (MPAs) [@klein_shortfalls_2015] as a case study to explore the implications of selecting one data set over the other.  Repeating the study using IUCN range data rather than AquaMaps data increases the apparent proportion of gap species from 1.4% to 6.4%, _while also increasing the proportion of well-protected species from 1.5% to 2.9%_ ___verify this second part!!!___.  This shift highlights the implications of different data use decisions on our understanding of marine biodiversity status and protection.
